---
title: "Week9-collab-doc"
format: html
editor: visual
---

load libraries

```{r}
library(tidyverse) #for data wrangling
library(lterdatasampler) #for data
library(ggeffects) #for model
library(here) #for easy file paths

```

Reading in data

```{r}
data(pie_crab)
```

I will visualize the data

```{r}
ggplot(aes(x = latitude, y = size),
       data = pie_crab) + #creating plot
  geom_point(color = "pink") + #scatterplot, pink points
  labs(x = "Latitude", y = "Size") + #update axis labels
  theme_minimal() #update theme to not have grid

```

Wrtitng a model here: 

```{r}
crab_model <- lm(size ~ latitude, # formula: response ~ predictor
                 data = pie_crab) # data frame

par(mfrow = c(2,2)) # display plots in 2x2 grid
plot(crab_model) # plot diagnostics 
```

run the model and interpret

```{r}
summary(crab_model) #look at model output
```

summarize our results:

slope: 0.49
y-intercept: -3.6 +/- 1.27

for every 1 increase in latitude, we expect to see a 0.49 increase in crab size +/- 0.034 mm.

model statistics: F(1,390) = 208.5, p < 0.001, alpha = 0.05, r^2^ = 0.35

General notes about collaboration: 
1. always save your changes! always commit and push your changes!
2. comment your code so that people know what you're doing
3. TALK TO YOUR COLLABORATORS!!
4. always pull before you start working in code!!!

